Report

### 2021-07-13 Rmd/report.Rmd
Add targets to workflow

```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="100%"}
means <- stimuli %>% 
	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	filter(location=="Barcelona") %>% 
	group_by(test_language, location, trial_type) %>% 
	summarise(familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
			  .groups = "drop") %>% 
	drop_na()

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	drop_na() %>% 
	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
	facet_wrap(~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Prime word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
means <- stimuli %>% 
	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	filter(location=="Barcelona") %>% 
	group_by(test_language, location, trial_type) %>% 
	summarise(familiarity_target = mean(familiarity_target, na.rm = TRUE),
			  .groups = "drop") %>% 
	drop_na()

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	drop_na() %>% 
	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
	facet_wrap(~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Target word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

>>>>

```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
means <- stimuli %>% 
	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, location, trial_type) %>% 
	summarise(
		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na()

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Prime word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
means <- stimuli %>% 
	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, location, trial_type) %>% 
	summarise(
		familiarity_target = mean(familiarity_target, na.rm = TRUE),
		.groups = "drop"
	)

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
	geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Target word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)
